---
title: "Curriculum Vitae"
author: "Jeffrey Scott Racine"
date: now
date-format: "YYYY-MM-DD"
bibliography: publications.bib
nocite: "@*"
format:
  html:
    toc: true
    include-in-header:
      - text: |
          <link rel="stylesheet" href="https://cdnjs.cloudflare.com/ajax/libs/font-awesome/6.4.0/css/all.min.css">
          <link rel="stylesheet" href="https://cdn.jsdelivr.net/npm/academicons@1.11.0/css/academicons.min.css">
          <style>
          /* Hide SVGs intended only for LaTeX/PDF output when rendering HTML */
          .latex-only { display: none !important; }
          </style>
  pdf:
    documentclass: article
    keep-tex: true
    number-sections: true
    geometry:
      - top=20mm
      - left=20mm
      - heightrounded
    include-in-header:
      - text: |
          \usepackage{fontawesome5}
          \usepackage{academicons}
          \usepackage[TU]{fontenc}
          \usepackage{caption}
          \usepackage{float}
pdf-engine: lualatex
knitr:
  opts_chunk:
    autodep: true
    collapse: true
    dev: "tikz"
    cache: false
    echo: false
    # eval.after: "fig.cap"
    fig.align: "center"
    # fig.asp: 0.65
    fig.pos: "H"
    # out.width: "85%"
    message: false
    warning: false
    R.options:
      np.messages: false
      plot.par.mfrow: false
## Create two variables to control display of Google Scholar section, one 
## controlling the Markdown header, the other controlling the R code chunks
params:
  gseval: true
header-gseval: true
---

## <i class="fa-solid fa-house"></i> Contact Information {.unnumbered}

-   <i class="fa-solid fa-paper-plane"></i> Department of Economics  
    Kenneth Taylor Hall, Room 426  
    McMaster University  
    1280 Main Street West  
    Hamilton, Ontario, Canada, L8S 4M4

-   [<i class="fa-solid fa-envelope"></i>](mailto:racinej@mcmaster.ca) racinej@mcmaster.ca

## <i class="fa-solid fa-globe"></i> Academic Profiles and Websites {.unnumbered}

-   [<i class="fa-brands fa-github"></i> ![](assets/github.svg){.latex-only width="1em" style="vertical-align:middle; display:none"} GitHub Profile: github.com/JeffreyRacine](https://github.com/JeffreyRacine)

-   [<i class="fa-solid fa-graduation-cap"></i> ![](assets/scholar.svg){.latex-only width="1em" style="vertical-align:middle; display:none"} Google Scholar Profile: scholar.google.com/citations?user=TXeKxGsAAAAJ](https://scholar.google.com/citations?user=TXeKxGsAAAAJ)

-   [<i class="fa-solid fa-globe"></i> ![](assets/globe.svg){.latex-only width="1em" style="vertical-align:middle; display:none"} IDEAS/RePEc Profile: ideas.repec.org/e/pra175.html](https://ideas.repec.org/e/pra175.html)

-   [<i class="fa-solid fa-globe"></i> ![](assets/impactstory.svg){.latex-only width="1em" style="vertical-align:middle; display:none"} Impactstory Profile: profiles.impactstory.org/u/0000-0002-5680-3705](https://profiles.impactstory.org/u/0000-0002-5680-3705)

-   [<i class="fa-solid fa-university"></i> ![](assets/mcmaster.svg){.latex-only width="1em" style="vertical-align:middle; display:none"} McMaster Website: experts.mcmaster.ca/display/racinej](https://experts.mcmaster.ca/display/racinej)

-   [![](assets/orcid.svg){width="1em" style="vertical-align:middle"} ORCID Profile: orcid.org/0000-0002-5680-3705](https://orcid.org/0000-0002-5680-3705)

-   [<i class="fa-solid fa-blog"></i> ![](assets/blog.svg){.latex-only width="1em" style="vertical-align:middle; display:none"} Personal Blog: jeffreyracine.github.io/blog](https://jeffreyracine.github.io/blog)

-   [<i class="fa-brands fa-researchgate"></i> ![](assets/researchgate.svg){.latex-only width="1em" style="vertical-align:middle; display:none"} ResearchGate Profile: www.researchgate.net/profile/Jeffrey_Racine](https://www.researchgate.net/profile/Jeffrey_Racine)

-   [<i class="fa-solid fa-globe"></i> ![](assets/scopus.svg){.latex-only width="1em" style="vertical-align:middle; display:none"} Scopus Profile: Author ID: 12790466400](https://www.scopus.com/authid/detail.uri?authorId=12790466400)

## Academic Background {.unnumbered}

## <i class="fa-solid fa-graduation-cap"></i> *Education:*

- Ph.D. Economics (1989), the University of Western Ontario, London, Canada (Aman Ullah, Supervisor)
- M.A. Economics (1985), McMaster University
- B.A. Economics (1984), *Summa Cum Laude*, McMaster University

- *Fields of Specialization:*
  - Econometrics and Statistics
  - Monetary Economics

- *Professional Affiliations:*
  - American Economic Association
  - American Statistical Association
  - Canadian Economics Association
  - Econometric Society
  - International Symposia for Nonparametric Statistics (ISNPS)

## Current Positions {.unnumbered}

-   Professor, Department of Economics, McMaster University (2005-)

-   Professor, Graduate Program in Statistics, Department of Mathematics and Statistics, McMaster University (2006-)

-   Senator William McMaster Chair in Econometrics, McMaster University (2005-)

-   Senior Research Associate, Info-Metrics Institute, American University, D.C., U.S.A (2010-)

-   Senior Fellow, Rimini Center for Economic Analysis, Rimini, Italy (2010-)

## Past Positions {.unnumbered}

-   International Research Fellow, CREATES, Aarhus University, Aarhus, Denmark (2013-2017)

-   Associate Department Chair, Department of Economics, McMaster University (2009-2011)

-   Associate Professor, Department of Economics, Syracuse University, Syracuse, U.S.A. (2002-2005)

-   Senior Research Associate, Center for Policy Research, Syracuse University, Syracuse, U.S.A. (2002-2005)

-   Associate Professor, Department of Economics, the University of South Florida, Tampa, U.S.A. (1999-2002)

-   Assistant Professor, Department of Economics, the University of South Florida, Tampa, U.S.A. (1993-1999)

-   Visiting Assistant Professor, Department of Economics, the University of California San Diego, San Diego, U.S.A. (1991-1993)

-   Assistant Professor, Department of Economics, York University, Toronto, Canada (1989-1993)

-   Instructor, Department of Economics, the University of Western Ontario, London, Canada (1986-1989)

-   Summer Intern, the International Monetary Fund, D.C., U.S.A (1988)

## <i class="fa-solid fa-award"></i> Honours and Awards {.unnumbered}

-   Fellow, *Journal of Econometrics* (2014-)

-   Editorial Fellow, *Econometric Reviews* (2018-)

-   *David J. and Helen C. Kahn Teaching Award* (the University of South Florida, 1997, $1,000)

-   *Outstanding Undergraduate Teaching Award* (the University of South Florida, 1997, $2,000)

-   *Sam Lawrence Prize in Labour Economics* (McMaster University, 1984, $225)

## <i class="fa-solid fa-book-open"></i> Editorial Positions {.unnumbered}

-   Guest Editor (with M. Gorfine and J. de Uña Álvarez), *Journal of Nonparametric Statistics*, ISNPS 2024 Special Volumes (2024-)

-   Associate Editor, [*Econometric Reviews*](http://www.tandfonline.com/action/journalInformation?show=editorialBoard&journalCode=lecr20), (2012-)

-   Deputy Editor-in-Chief, [*Econometrics*](http://www.mdpi.com/journal/econometrics/editors), (2016-2019)

-   Associate Editor, [*Journal of Econometric Methods*](http://www.degruyter.com/view/j/jem), (2010-2018)

-   Editorial Board, *Book Series on Econometrics*, World Scientific and Imperial College Press, (2013-)

-   Editor (with L. Su and A. Ullah), *Oxford Handbook of Semiparametric and Nonparametric Econometric Methods*, (2011-2014)

-   Guest Editor (with Q. Li), *Advances in Econometrics*, Volume 24, Nonparametric Methods (2009-2010)

## Visiting Appointments {.unnumbered}

-   Visiting Fellow, ENSAI ($\acute{\text E}$cole nationale de la statistique et de l'analyse d l'information), Rennes, France (2022)

-   Visiting Fellow, ENSAI ($\acute{\text E}$cole nationale de la statistique et de l'analyse d l'information), Rennes, France (2016)

-   Visiting Fellow, CSIR (Council for Scientific and Industrial Research), Pretoria, South Africa (2016)

-   Visiting Fellow, ENSAI ($\acute{\text E}$cole nationale de la statistique et de l'analyse d l'information), Rennes, France (2015)

-   Visiting Fellow, CREATES, Aarhus University, Aarhus, Denmark (2015)

-   Visiting Research Scholar, the University of Melbourne, Melbourne, Australia (2014)

-   Visiting Fellow, CREATES, Aarhus University, Aarhus, Denmark (2014)

-   Visiting Fellow, Cowles Foundation, Yale University, New Haven, U.S.A. (2014)

-   Visiting Fellow, QuanTM Institute, Emory University, Atlanta, U.S.A. (2013)

-   Visiting Fellow, CREATES, Aarhus University, Aarhus, Denmark (2011)

-   Visiting Fellow, the Toulouse School of Economics, Toulouse, France (2011)

-   Visiting Fellow, GREMAQ, the Toulouse School of Economics, Toulouse, France (2010)

-   Visiting Fellow, Info-Metrics Institute, American University, D.C., U.S.A. (2010)

-   Visiting Fellow, GREMAQ, the Toulouse School of Economics, Toulouse, France (2008)

-   Visiting Fellow, Department of Economics and Finance, La Trobe University, Melbourne, Australia (2008)

-   Visiting Fellow, Centre interuniversitaire de recherche en économie quantitative, McGill University, Montreal, Canada (2007)

-   Visiting Fellow, Mathematical Sciences Institute, the Australian National University, Canberra, Australia (2002)

## Courses Taught {.unnumbered}

-   *Graduate:*
    - Econometrics I
    - Econometrics II
    - Econometrics III
    - Topics in Econometrics
    - Advanced Topics in Econometrics
    - Advanced Econometrics

-   *Undergraduate:*
    - Managerial Economics
    - Introduction to Money and Banking
    - International Monetary Economics
    - Monetary Economics
    - Introduction to Macroeconomics
    - Introduction to Microeconomics
    - Intermediate Price Theory
    - Intermediate Microeconomic Theory I
    - Introductory Mathematical Statistics I
    - Introductory Mathematical Statistics II
    - Econometrics I
    - Econometrics II
    - Analysis of Economic Data I

-   *Independent Studies:*
    - Nonparametric Kernel Estimation (1997)

## Ph.D. Candidate Supervision and Examination {.unnumbered}

-   *Thesis Supervisor:*

    1.  Ugarte Bravo, Karen (2022, Economics, McMaster University, as of Fall 2021 on faculty in the Department of Economics at the University of Toronto)

    2.  Sexton, Sean (2022, Economics, McMaster University, as of Summer 2022 Part-Time Instructor in the Department of Statistics, University of Toronto)

    3.  Simardone, Camille (2021, Economics, McMaster University, as of Fall 2021 on faculty in the Department of Economics at the University of British Colombia, Okanagan Campus)

    4.  Kiwon, Francis (2019, M.Sc., Mathematics (Statistics), McMaster University, currently a Ph.D. student in the Department of Statistics at the University of Waterloo, Canada)

    5.  Clair, Luc (2017, Economics, McMaster University, currently on faculty at the University of Winnipeg, Canada)

    6.  Kealey, John (2016, Economics, McMaster University)

    7.  Thompson, John (2014, M.Sc., Mathematics (Statistics), McMaster University, as of Fall 2021 on faculty in the Department of Mathematics at the University of British Colombia, Okanagan Campus)

-   *Thesis Committee Member:*

    1.  Roberts, Keith (2025-, Economics, McMaster University)

    2.  Neal, Mackenzie (2023-, Mathematics (Statistics), McMaster University)

    3.  Owusu, Julius (2023, Economics, McMaster University, currently on faculty at the University of Bristol, England)

    4.  Gallaugher, Michael (2020, Mathematics (Statistics), McMaster University, currently Banting Fellow on faculty at Baylor University, Texas U.S.A.)

    5.  Shamsi, Azam (2018, School of Business, McMaster University, currently on faculty at the University of New Brunswick, Canada)

    6.  Thomas, Stephanie (2016, Economics, McMaster University, currently on faculty at Curtin University, Australia)

    7.  Olagunju, Waheed (2016, Economics, McMaster University, currently working at the King Abdullah Petroleum Studies and Research Center, Saudi Arabia)

    8.  Tellez, Juan (2014, Economics, the University of Geneva, currently a Post-Doctoral Fellow at the Harvard Kennedy School, U.S.A.)

    9.  Meredith, Evan (2012, Mathematics (Statistics), McMaster University, currently working at Human Services Alberta, Canada)

    10. Li, Jinhu (2011, Economics, McMaster University, currently on faculty at the University of Melbourne, Australia)

    11. McLeod, Logan (2010, Economics, McMaster University, currently on faculty at Wilfrid Laurier University, Canada)

    12. de Oliveira, Claire (2008, Economics, McMaster University, currently on faculty at the University of York, UK)

    13. Liu, Long (2008, Economics, Syracuse, currently on faculty at the University of Texas at San Antonio, U.S.A.)

    14. Dammert, Ana (2006, Economics, Syracuse, currently on faculty at Carleton University, Canada)

    15. Galdo, Jose (2006, Economics, Syracuse, currently on faculty at Carleton University, Canada)

        \[NB - from 1993-2002 I was a faculty member in the Department of Economics at the University of South Florida and, at that time, they did not have a Ph.D. program\]

    16. Papanastasiou, John (1992, Economics, York, currently on faculty at the University of Macedonia, Thessaloniki, Greece)

-   *Thesis External Examiner:*

    1.  Håkon Otneim (2016), Mathematics, the University of Bergen, Norway.

    2.  Henpitahewage Thilaksha Tharanganie (2015), Econometrics and Business Statistics, Monash University, Australia.

    3.  Marcos Gómez (2011), Economics, Universidad de Zaragoza, España.

    4.  Lindsay Tedds (2005), Economics, McMaster University.

    5.  Yulia Kotlyarova (2005), Economics, McGill University, Canada.

    6.  Dingding Li (2002), Economics, the University of Guelph, Canada.

## University Service {.unnumbered}

-   *McMaster University:*
    - Ad Hoc Selection Committee for IT Support in the Faculty of Social Sciences (2013)
    - Ad Hoc Selection Committee for the Director of the School of Social Work (2009, 2025)
    - Faculty Multimedia Computing and Electronic Communication Committee (2005-)
    - Faculty of Social Sciences' Tenure and Promotion Committee (2009-2012, 2012-2015, 2019-2020, 2020-2023)
    - Graduate Admissions Committee (2005-2007)
    - Hiring Committee (2005-2007)
    - Research High-Performance Computing Support Committee (2005-)
    - Research Information Technology Committee (2020-)
    - Selection Committee for Replacement for Technical Director for Research High-Performance Computing Support (2011-2012)
    - Selection Committee for the Director of the Masters in Statistics Programme (2009)
    - Selection Committee for Director, Research & High Performance Computer Support (2021)
    - Tenure and Promotion Task Force (2012)
    - Tenure and Promotion Committee (2005-2007, 2017-2018, 2023-2024)
    - Tenure and Promotion University Secretariat (2019-)
    - University Scholar Committee (2025)

-   *Syracuse University:*
    - Econometrics Seminar Series Coordinator (2002-2005)
    - Executive Committee (2003-2005)
    - Freshman Forum Adviser (2003)
    - ICT Advisory Committee (2003-2005)
    - Research Evaluation Committee (2002-2005)
    - Statistics Program Review Committee (2003)
    - Tenure and Promotion Committee (2002-2005)

-   *The University of South Florida:*
    - Committee on Scholarship (2000-2001)
    - Economics Department Committee A (1999-2000, 2001-2002)
    - Economics Department Computing Coordinator (1993-2002)
    - Outstanding Undergraduate Teaching Award Committee (1998)

-   *York University:*

    Economics Department Computing Coordinator (1989-1992)

## External Service {.unnumbered}

-   *Social Sciences and Humanities Research Council of Canada (CRSH/SSHRC)*

    Insight Grants Committee, Chair, (2013-2014).

-   *International Symposia for Nonparametric Statistics (ISNPS)*
    - Member of Board of Directors (Elected 5/21/2018-)
    - Member of Council Committee (Elected 1/1/2016-)
    - Member of Charting Committee (2011-2015)
    - Charting Committee, 2012 Annual Meetings (June 15-19, 2012, Chalkidiki, Greece)
    - Charting Committee, 2014 Annual Meetings (June 12-16, 2014, Cádiz, España)
    - Scientific Committee, 2024 Annual Meetings (June 25-29, 2024, Braga, Portugal)
    - Scientific Committee, 2026 Annual Meetings (June 22-26, 2026, Thessaloniki, Greece)

-   *Info-Metrics Institute*
    - Memorial Prize Committee in Memory of Halbert L. White, Jr., (2016-)
    - Organizing Committee for the 2012 Workshop on Nonparametric Inference (November 17, 2012, the University of California, Riverside)

-   *Compute/Calcul Canada*
    - National Resource Allocation Committee (2009-)

-   *American Statistical Association*
    - Publications Committee (2009)

-   *SHARCNET*
    - Resource Allocation Committee Chair, Round VI & VII (2007)
    - Site Representative (2008-)

## Grants and Fellowships {.unnumbered}

1.  Social Sciences and Humanities Research Council of Canada - *Insight Grant*

    Title: *A Foundational Framework For Functional Data Analysis*
    Amount: $103,883
    Date: March 28, 2025 - March 31, 2030

2.  Social Sciences and Humanities Research Council of Canada - *Insight Grant*

    Title: *A Comprehensive Framework for Model Averaging*
    Amount: $176,593
    Date: March 15, 2018 - March 31, 2023

3.  McMaster (RHPCS) Research Software Pilot Project

    Title: The R package np
    Amount: In kind programming
    Date: Fall 2019 - Winter 2020

4.  Social Sciences and Humanities Research Council of Canada - *Insight Grant*

    Title: *A Unified Framework for Nonparametric Instrumental Variable Estimation*
    Amount: $206,729
    Date: July 1, 2013 - June 30, 2018

5.  Social Sciences and Humanities Research Council of Canada - *Standard Research Grant*

    Title: *Adaptive Robust Kernel Estimation*
    Amount: $93,000 ($78,000 SSHRC, $15,000 McMaster University matching funds)
    Date: July 1, 2009 - June 30, 2012

6.  Canadian Institutes of Health Research - *Health Services and Policy Research Operating Grant*

    Joint with Paul V. Grootendorst
    Title: *Assessment of the Cost and Equity of Different Catastrophic Drug Insurance Options for Canadians*
    Amount: $233,669
    Date: September 1, 2008 - August 30, 2010

7.  Social Sciences and Humanities Research Council of Canada - *Standard Research Grant*

    Title: *Kernel Estimation of a Conditional CDF with Mixed Data*
    Amount: $108,630 ($93,630 SSHRC, $15,000 McMaster University matching funds)
    Date: July 1, 2005 - June 30, 2008

8.  Canadian Institutes of Health Research - *Health Services and Policy Research Operating Grant*

    Joint with Carlos R. Quiñonez, David Locker, Peter V. Cooney, Raisa B. Deber, Paul V. Grootendorst, Stephen W. Hwang, and Sunjay Suri
    Title: *Alleviating disparities in oral health: Responding to the information needs of key decision makers (and the KT plan)*
    Amount: $109,900
    Date: January 1, 2008 - December 31, 2008

9.  Natural Sciences and Engineering Research Council of Canada - *Discovery Grant*

    Title: *Real Time Kernel Estimation*
    Amount: $12,000
    Date: July 1, 2005 - June 30, 2006

10. National Science Foundation - *Major Research Instrumentation Grant: Principal Investigator*

    Title: *Acquisition of a Beowulf Class Cluster Computer to Support Interdisciplinary Faculty Research*
    Amount: $162,810 ($113,967 NSF, $48,843 Syracuse University required cost-share)
    Date: August 1, 2003

11. USF Division of Sponsored Research - *Research and Creative Scholarship Award*

    Title: *Nonparametric Hypothesis Testing in the Presence of Mixed Discrete and Continuous Data Types*
    Amount: $7,500
    Date: January 1, 2001 - December 31, 2001

12. National Institute of Health - *Research Grant*

    Title: *Advanced Statistical Tools for Biomedical Research*
    Amount: $20,000
    Date: May 1, 1999 - December 31, 2000

13. USF Division of Sponsored Research - *Research and Creative Scholarship Award*

    Title: *Density-Based Multinomial Choice - Theory and Applications*
    Amount: $7,500
    Date: January 1, 1999 - December 31, 1999

14. USF Division of Sponsored Research - *Research and Creative Scholarship Award*

    Title: *Finite-Sample Corrections for* $hv$-Block Cross-Validation
    Amount: $7,500
    Date: January 1, 1997 - December 31, 1997

15. National Science Foundation SBR Grant - *Research Grant*

    Co-Collaborator with Halbert White, Principal Investigator
    Title: *Improved Estimation and Specification Testing with Parametric, Nonparametric, and Neural Network Models Using the Bootstrap*
    Amount: $166,650
    Date: August 1, 1995 - July 31, 1998

16. USAF Phase II Standards Technology Transfer Network - *Research Grant*

    Title: *Automatic Data Modeling*
    Amount: $29,000
    Date: May 6, 1996 - July 25, 1998

17. USF Division of Sponsored Research - *Research Grant*

    Title: *Testing Exchange Market Efficiency using Nonparametric and Nonlinear Estimation*
    Amount: $6,500
    Date: January 1, 1995 - December 31, 1995

18. Social Sciences and Humanities Research Council of Canada - *Operating Grant*

    Title: *Semiparametric Estimation of Multi-Equation Econometric Models*
    Amount: $15,000
    Date: June 1, 1992 - June 1, 1995

19. Natural Sciences and Engineering Research Council of Canada - *Research Grant*

    Title: *Estimation of Multivariate Systems Models: A Heteroscedasticity-Consistent Approach*
    Amount: $27,000
    Date: April 1, 1991 - April 1, 1994

20. Social Sciences and Humanities Research Council of Canada - *Strategic Grant*

    Joint work with D. Shapiro, J.B. Smith, and M. Stelcner
    Title: *The Gender Earnings Gap and Labour Market Discrimination in Canada: A Reassessment and Extension of Econometric and Policy Analysis*
    Amount: $20,000
    Date: October 1, 1990 - September 31, 1992

21. Social Sciences and Humanities Research Council of Canada - *Doctoral Fellowship*

    Amount: $12,500 per annum
    Date: 1987-1988, 1988-1989

22. Ontario Graduate Scholarship - *Doctoral Scholarship*

    Amount: $8,500
    Date: 1985-1986
    
::: {.content-visible when-meta="header-gseval"}
## <i class="ai ai-google-scholar"></i> Google Scholar Citation Summary {.unnumbered}
:::

<center>

```{r, eval=params$gseval}
#| label: foopander
#| message: FALSE
#| warning: FALSE
#| echo: FALSE
#| results: 'asis'
## Re-use foo below to do counting etc. and can't use formatted
## version for this, so make copy (foofoo) for formatting big.mark
## comma in table then can re-use foo later for counts etc.
foofoo <- foo <- gcite::gcite_user_info('TXeKxGsAAAAJ',verbose=FALSE,read_citations=FALSE)
#foofoo$citation_indices$`All` <- format(foofoo$citation_indices$`All`,big.mark=",")
#foofoo$citation_indices$`Since 2019` <- format(foofoo$citation_indices$`Since 2019`,big.mark=",")
foofoo$citation_indices[[2]] <- format(foofoo$citation_indices[[2]],big.mark=",")
foofoo$citation_indices[[3]] <- format(foofoo$citation_indices[[3]],big.mark=",")
pander::panderOptions('table.alignment.default',c('left','right','right'))
pander::pander(foofoo$citation_indices)
```

</center>

```{r, eval=params$gseval}
#| label: fooplot
#| message: FALSE
#| fig-asp: 0.4
#| out-width: "75%"
#| warning: FALSE
#| echo: FALSE
#| results: 'asis'
require(ggplot2)
require(gridExtra)
require(scholar)
#plot1 <- qplot(1)
#plot2 <- qplot(1)
## Adjust for discrepancy in total (field All[1] in call to gcite)
adjust <- foo$citation_indices$All[1]-sum(foo$overall_citations$n_citations)
plot1 <- ggplot(foo$overall_citations,aes(x=year,y=n_citations))+
    geom_bar(stat='identity')+
    theme_bw()+
    xlab('Year')+
    ylab('Citations/Year')
plot2 <- ggplot(foo$overall_citations,aes(x=year,y=cumsum(n_citations)+adjust))+
    geom_bar(stat='identity')+
    theme_bw()+
    xlab('Year')+
    ylab('Cumulative Citations')
grid.arrange(plot1, plot2, ncol=2)    
```

## <i class="fa-solid fa-book"></i> Books {.unnumbered}

-   Racine, J.S. (2019), *An Introduction to the Advanced Theory and Practice of Nonparametric Econometrics (A Replicable Approach Using R),* Cambridge University Press, ISBN 9781108483407, 408 pages.

-   Racine, J.S. (2019), *Reproducible Econometrics Using R,* Oxford University Press, ISBN: 9780190900663, 293 pages.

-   Li, Q. and J.S. Racine (2007), *Nonparametric Econometrics: Theory and Practice,* Princeton University Press, ISBN: 9780691121611, 746 pages.

    Chinese Edition:

    Li, Q. and J.S. Racine (2015), *Nonparametric Econometrics: Theory and Practice,* Translated by Ye Azhong, Wu Xiangbo et al., Peking University Press, ISBN: 9787301249673.

## <i class="fa-solid fa-book-open"></i> Edited Volumes {.unnumbered}

-   *Nonparametric Econometric Methods* (2009), Volume 25 of the book series: Advances in Econometrics, ISBN: 9781849506236, Edited by: Qi Li, Jeffrey S. Racine.

-   *Oxford Handbook of Semiparametric and Nonparametric Econometric Methods* (2014), ISBN 9780199857944, Edited By Jeffrey S.\u00A0Racine, Liangjun Su, and Aman Ullah.

## \faRProject\u00A0Packages {.unnumbered}

-   The `np' package for R available directly from the Comprehensive R Archive Network <https://cran.r-project.org/web/packages/np/index.html>.

-   The `npiv' package for R available directly from the Comprehensive R Archive Network <https://cran.r-project.org/web/packages/npiv/index.html>.

-   The `npRmpi' package for R available directly from the Comprehensive R Archive Network <https://cran.r-project.org/web/packages/np/index.html>.

-   The `crs' package for R available directly from the Comprehensive R Archive Network <https://cran.r-project.org/web/packages/crs/index.html>.

-   The `ma' package for R <https://github.com/JeffreyRacine/R-Package-ma>.

-   The `hr' package for R <https://github.com/JeffreyRacine/R-Package-hr>.

## Peer Reviewed Publications {.unnumbered}

1.  @patilea_inpress_locally
1.  @racine_inpress_quarto
1.  @wang_2025_bootstrap
1.  @racine_2024_boundary
1.  @hansen_2024_bootstrap
1.  @du_2024_shape
1.  @racine_2023_optimal
1.  @simardone_2021_nonparametri
1.  @racine_2020_kernel
1.  @ma_2020_nonparametri
1.  @racine_2020_kernel
1.  @racine_2019_energy
1.  @parmeter_2019_nonparametri
1.  @beheshti_2019_information
1.  @li_2018_optimal
1.  @das_2018_interactive
1.  @florens_2018_nonparametri
1.  @centorrino_2017_semiparametr
1.  @racine_2017_nonparametri
1.  @li_2017_cross
1.  @kiefer_2017_the
1.  @koch_2016_health
1.  @racine_2016_local
1.  @bugden_2016_nonparametri
1.  @maasoumi_2016_a
1.  @chakrabarty_2015_household
1.  @ma_2015_spline
1.  @hall_racine_2015_infiniteorder
1.  @racine_2015_mixeddata
1.  @gao_liu_racine_2015_partiallylinear
1.  @gyimahbrempong_2014_aid
1.  @racine_parmeter_2014_data_driven
1.  @du_parmeter_racine_2013_constrained
1.  @li_lin_racine_2013_optimalbandwidth
1.  @li_lin_racine_2013_optimalbandwidth
1.  @ma_racine_2013_additive2
1.  @li_lin_racine_2013_optimalbandwidth
1.  @nie_racine_2012_crs
1.  @parmeter_racine_2012_frontier
1.  @racine_2012_rstudio
1.  @hansen_racine_2012_jackknife
1.  @gyimahbrempong_2012_aid
1.  @zhang_chen_liu_racine_2011_disease
1.  @racine_2011_chapter
1.  @li_racine_2010_smoothvarying
1.  @gyimahbrempong_2010_aid
1.  @racine_2009_nonparametric_methods_in_r
1.  @li_maasoumi_racine_2009_test
1.  @kiefer_racine_2009_smoothreverend
1.  @li_maasoumi_racine_2009_test
1.  @meredith_racine_2009_reproducible
1.  @li_maasoumi_racine_2009_test
1.  @ouyang_li_racine_2009_nonparamregression
1.  @maasoumi_racine_2009_entropy
1.  @li_racine_2008_maxima
1.  @hayfield_racine_2008_np
1.  @li_racine_2008_maxima
1.  @li_racine_2008_maxima
1.  @racine_2008_primer
1.  @hall_racine_2007_infinite
1.  @hayfield_racine_2007_np
1.  @hsiao_li_racine_2007
1.  @racine_mackinnon_2007_bootstrap_p
1.  @racine_mackinnon_2007_bootstrap_p
1.  @racine_mackinnon_2007_bootstrap_p
1.  @maasoumi_racine_2007_entropy
1.  @chakrabarty_schmalenbach_racine_2006
1.  @racine_kern_2006_testing
1.  @gyimahbrempong_2006_alcohol
1.  @racine_kern_2006_testing
1.  @racine_kern_2006_testing
1.  @racine_kern_2006_testing
1.  @ouyang_li_racine_2006
1.  @racine_2004_parallel
1.  @hall_li_racine_2004
1.  @li_racine_2004_crossval
1.  @granger_maasoumi_racine_2004
1.  @li_racine_2004_crossval
1.  @racine_2004_parallel
1.  @li_racine_2003_multivariate
1.  @racine_2002_directmarketing
1.  @racine_2002_directmarketing
1.  @maasoumi_racine_2002_entropy
1.  @racine_2002_directmarketing
1.  @racine_2002_directmarketing
1.  @racine_2002_directmarketing
1.  @racine_2001_biascorrected
1.  @white_racine_2001_nn
1.  @chen_racine_swanson_2001
1.  @racine_2001_biascorrected
1.  @racine_2000_feasible_resampling
1.  @racine_2000_feasible_resampling
1.  @racine_2000_feasible_resampling
1.  @racine_2000_feasible_resampling
1.  @racine_1997_hvblock
1.  @racine_1997_hvblock
1.  @morrow_stein_racine_1997_videokeratography
1.  @racine_rilstone_1995_reverse
1.  @gonzalez_rivera_racine_1995_garch
1.  @racine_1993_efficient
1.  @ullah_racine_1992_smooth

## Published Book Reviews {.unnumbered}

-   Racine, J.S.\u00A0(2005), "Finite Sample Econometrics by Aman Ullah," *Economic Record*, Volume 81, Issue 1, pages 94-95.

-   Racine, J.S.\u00A0(2001), "Nonparametric Econometrics - Themes in Modern Econometrics by Adrian Pagan and Aman Ullah," *Journal of The American Statistical Association*, March, Volume 96, Number 453, pages 343-345.

## Work Submitted for Publication {.unnumbered}

-   Chen, X., T. Christensen, S. Kankanala and J.S. Racine, "npiv: Estimation and Inference for Nonparametric Instrumental Variables Models Using R," submitted for publication.

```{=html}
<!--

- Smits, J. and J.S.\ Racine, "Testing Exclusion Restrictions in Nonseparable Triangular Models," submitted for publication.

- Grootendorst, P.\ and J.S.\ Racine, "Distributional Effects of Needs-Based Drug Subsidies: Regional Evidence From Canada," submitted for publication.

-->
```

## Workshops {.unnumbered}

... (rest of document unchanged)

## References {.unnumbered}

::: {#refs}
:::
